Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-16 chapters/introduction/introduction.tex
more changes on background.

\begin{itemize}[noitemsep]
\item \textbf{Geo-Localization:}
Extracting location-dependent or orientation-dependent features from
image data has drawn a great detail of attention from the vision
community~\cite{jacobs07geolocate, jacobs11geolocate,
jacobs08geoorient}. The common trend amongst these methods is that
they take advantage of a large dataset of geo-referenced images. Hays
and Efros~\cite{hays2008im2gps} use a data-driven scene matching
approach to localize a query image using a large dataset of geo-tagged
images.  Doersch \etal~\cite{doersch2012what} extract
location-dependent features that capture the relative appearance
differences of large cities.  Lin et al.~\cite{lin2013cross} localize
a ground-level image by learning the relationship between pairs of
ground and aerial images of the same location. Other techniques focus
on urban environments and infer location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
estimate camera pose. Many other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.
\newline

@@

\subsection{Ground-to-Aerial Geo-Calibration}
Data-driven scene matching approaches are widely used to localize a
query image by registering in a large dataset of geo-tagged
images~\cite{im2gps, li2010location,zamir2010accurate}.
Benefited from the fast growing monitoring satellite and drone markets,
geo-tagged satellite/aerial imagery becomes more and more available
than ever before, which makes it a rich source for building
reference database. We refer to the geo-calibration methods which use
the aerial imagery as geographic reference as {\em Ground-to-Aerial
Geo-Calibration}.

Cross-view image pair is the basic element for ground-to-aerial
geo-calibration. It consists of a ground-level image and an overhead
image at the same location. In some cases, two images may also be aligned
in orientation.

Recent work on ground-to-aerial
geo-localization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
has shown that convolutional neural networks are capable of extracting
features from geo-tagged aerial imagery that can be matched to features extracted
from the inquiry ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
line of work, demonstrating improved geo-localization performance by
applying an auxiliary loss function to regress the ground-level camera
orientation with respect to the aerial image. Hu and Feng
\etal~\cite{mh2018cvm} achieve the state-of-the-art performance in
geo-localization by extracting cross-domain global features using
the NetVLAD~\cite{arandjelovic2016netvlad} technique.

>>>>

\begin{itemize}[noitemsep]
\item \textbf{Geo-Localization:}
Extracting location-dependent or orientation-dependent features from
image data has drawn a great detail of attention from the vision
community~\cite{jacobs07geolocate, jacobs11geolocate,
jacobs08geoorient}. The common trend amongst these methods is that
they take advantage of a large dataset of geo-referenced images. Hays
and Efros~\cite{hays2008im2gps} use a data-driven scene matching
approach to localize a query image using a large dataset of geo-tagged
images.  Doersch \etal~\cite{doersch2012what} extract
location-dependent features that capture the relative appearance
differences of large cities.  Lin et al.~\cite{lin2013cross} localize
a ground-level image by learning the relationship between pairs of
ground and aerial images \footnote{In the context of our thesis, we
do not distinguish between the satellite imagery and the aerial
imagery} of the same location. Other techniques focus
on urban environments and infer location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
estimate camera pose. Many other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.
\newline

@@

\subsection{Ground-to-Aerial Geo-Calibration}
Data-driven scene matching approaches are widely used to for
geo-calibration.
When localizing a camera, data-driven algorithms search for k-nearest
neighbors of the query image in the database of the geo-tagged imagery.
To reduce the work of querying, the searching process is usually
carried out in some feature space with applicable number of  
dimensions~\cite{im2gps, li2010location,zamir2010accurate}.
However, as items found in most reference dataset, geo-tagged
ground-level images collected from the internet are usually noisy and
sparse in geographic space. To achieve more accurate geo-calibration
results, we need alternative image resources with more accurate
geographic tags and denser spatial coverage.

Benefited from the fast growing monitoring satellite and drone markets,
the geo-tagged aerial imagery becomes more publicly accessible
than ever before. Aerial imagery downloading services like
Microsoft Bing Map provide aerial images of various
resolutions, which can cover most areas of the world with accurate
geographic tags, making aerial imagery a rich source for
reference database. We refer to the geo-calibration methods
which use the aerial imagery as geographic reference as
ground-to-aerial geo-calibration.

Recent work on ground-to-aerial
geo-calibration~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
has shown that convolutional neural networks are capable of extracting
features from geo-tagged aerial imagery that can be matched to
features extracted from the ground imagery.  Vo
\etal~\cite{vo2016localizing} extend this line of work, demonstrating
improved geo-localization performance by applying an auxiliary loss
function to regress the ground-level camera orientation with respect
to the aerial image. Hu and Feng \etal~\cite{mh2018cvm} achieve the
state-of-the-art performance in geo-localization by extracting
cross-domain global features using the
NetVLAD~\cite{arandjelovic2016netvlad} technique.
